Supplementary Materials for: ``Well-Designed Environmental Markets Enable Large-Scale Marine Conservation''

### 2019-10-28 docs/Supplementary_materials.tex
Updated supplementary materials

%% TABLE FOR NUMERIC VARIALBES
\begin{table}[H]
\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Displaced & Non-displaced & Difference\\
\hline
Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
\hline
Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
\hline
Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
\hline
PNA fishing in 2014 (hours) & 667.57 (489.24) & 529.33 (380.11) & -138.24 (-1.89) *\\
\hline
Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{img/plw_2018.png}
\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution. The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively. Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
\end{figure}

>>>>

%% TABLE FOR NUMERIC VARIALBES
\begin{table}[H]
\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks indicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Displaced & Non-displaced & Difference\\
\hline
Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
\hline
Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
\hline
Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
\hline
PNA fishing in 2014 (hours) & 667.57 (489.24) & 529.33 (380.11) & -138.24 (-1.89) *\\
\hline
Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{img/plw_2018.pdf}
\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution. The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively. Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
\end{figure}
